---
title: "Assignment3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(devtools)
library(roxygen2)
```

## Instructions

*a table that has prices for different fish
* a table that has the number caught for each fish
species for each location
* each location is in a different column
* each fish is in a different row 

Function output will be

* most frequently caught fish in each location
* total revenue for each location
* total fisheries revenue sum

* if user requests it graph of revenue by location and total revenue (as text)

## Function definition and example data, where you generate the data yourself

Note that I'm showing here but should be stored in a *.R file
And then generate data

```{r fdefin}



# create a list of possible fish to sample from
possible_fish = c("squid","cod","lobster","salmon","caplin")

# generate typical prices for each possible fish
prices = data.frame(fish=possible_fish, price=c(2,3,10,5,1))

locs = c("SB","LA","PS","SB2","LA2")
example_catch = matrix(nrow=length(possible_fish), ncol=length(locs) )
colnames(example_catch)=locs
rownames(example_catch)=possible_fish

# lets simulate different productivities or typical size of catch in this area
locs = data.frame(name=locs, size = c(1000,1000.5000,2000,3000,500))

# and different relative population size for fish


for ( i in 1: length(possible_fish)) {
  for (j in 1:nrow(locs)) {
      example_catch[i,j] =  round(rnorm(mean=locs$size[j], sd=0.1*locs$size[j], n=1))
  }
}
  
# run function
fisheries_summary(catches=example_catch, prices=prices, plot=FALSE)

# try with a plot
fisheries_summary(catches=example_catch, prices=prices, plot=TRUE)



```



You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
